Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2019-02-09 pkg/disttree/inst/draft/rejoinder2.Rnw
further revisions regarding the comment of the AE in the main manuscript and the rejoinder
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2458 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 3d50f9000476a0f25edaf2e24265d953cb86472f

FIXME: adaption in the manuscript

FIXME: I think we should present the two arguments more side by side, i.e., mention both
early on and subsequently discuss both in more detail. (1) One factor is that only a single
split into 28 years of training and 4 years of test data is considered in the main manuscript.
When doing the full cross-validation the pronounced differences between the methods are much
diminished. (2) East Tyrol is in a different climate zone and hence effects could be more
additive and with less interactions than in North Tyrol.

Thank you very much for your comment! East Tyrol lies in a different climate zone than the 
rest of Tyrol indicating different meteorological characteristics. For example, a covariate
might have a linear effect on the expected amount of rain in East Tyrol while it has a
non-additive effect in Northern Tyrol. In this case, in East Tyrol an additive model such as 
GAMLSS will capture this influence better than a tree model, particularly if this covariate
is correctly specified in the model (which might be the case in the prespecified GAMLSS).
Of course, these are just assumptions and there could be many other reasons. However,
looking at the results of the cross-validation in Supplement~B it can be observed that
the difference in performance between the GAMLSS and the distributional forest models as
seen in the single evaluation evens out, hence the specific choice of learning years seems
to have an impact as well.

>>>>

% FIXME: adaption in the manuscript

% FIXME: I think we should present the two arguments more side by side, i.e., mention both
% early on and subsequently discuss both in more detail. (1) One factor is that only a single
% split into 28 years of training and 4 years of test data is considered in the main manuscript.
% When doing the full cross-validation the pronounced differences between the methods are much
% diminished. (2) East Tyrol is in a different climate zone and hence effects could be more
% additive and with less interactions than in North Tyrol.

Thank you very much for your comment! One important fact that could be a reason for the
different results is that East Tyrol does not lie in the same climate zone as the rest of Tyrol 
indicating different meteorological characteristics. For example, a covariate
might have a linear effect on the expected amount of rain in East Tyrol while it has a
non-additive effect in Northern Tyrol. In this case, in East Tyrol an additive model such as 
GAMLSS will capture this influence better than a tree model, particularly if this covariate
is correctly specified in the model (which might be the case in the prespecified GAMLSS).
Of course, this is just an assumption and there could be other reasons for the performance
difference between the GAMLSS and the distributional forest models in East Tyrol. However, 
looking at the results of the cross-validation in Supplement~B it can be observed that this 
difference as seen in the single evaluation evens out for several stations in East Tyrol, 
hence the specific choice of learning and validation period seems to have an impact as well.
These two aspects are now also discussed more in detail in the main manuscript.
